---
title: "Tutorial and Comparison"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial and Comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stats)
library(datasets)
library(zmjianglm)
```


## Introduction
The main function `mylm` is trying to do the linear regression procedures including estimation and inference and get some important values. `mylm` combines `lm` and `summary.lm` in pacakge `stats` together. Users can choose to print or not to print the output and can also choose either a simple version or a complete version to print. The simple version is similar to the output of `lm` and the complete version is similar to the output of `summary.lm`. The function would return a list of elements which is almost the same as `summary.lm` no matter what printing style is chosen.
And the function `predictlm` is written for get predicted value in a new data set based on the fitted model.
The example data set is `mtcars`, which is included in package `datasets`. More information could be viewed by:

```{r,eval=FALSE}
?mtcars
```

## Usage
### Usage of `mylm`
To use the function `mylm`:
```{r}
mylm(mpg~wt,mtcars,"nothing")
```
To print out the simple version of output:
```{r}
mylm(mpg~wt,mtcars,"simple")
```
To print out the complete version of output:
```{r}
mylm(mpg~wt,mtcars,"summary")
```
Do multiple linear regression:
```{r}
mylm(mpg~wt+drat,mtcars,"summary")
```
Add categorical covariate:
```{r}
mylm(mpg~wt+drat+factor(cyl),mtcars,"summary")
```
Add interaction term:
```{r}
mylm(mpg~wt+drat+I(wt*drat),mtcars,"summary")
```
Do transformation on covariate:
```{r}
mylm(mpg~wt+drat+I(wt^2),mtcars,"summary")
```

### Usage of `predictlm`
To use function `predictlm`
```{r}
n <- nrow(mtcars)
train_n <- floor(n*0.7)
traindata <- mtcars[1:train_n, ]#the original data set
testdata <- mtcars[(train_n+1):n, ]#the new data set

mylm1 <- mylm(mpg~wt,traindata,"nothing")
predicted_value <- predictlm(mylm1,testdata)
```

## Comparison
### Correctness
The correctness is tested by `testthat`. All the tests are passed. Basically, I compared the result of `summary.lm` and `mylm` as well as the result of `predict.lm` and `predictlm`. The example of correctness testing is as the following: 
```{r}
#mylm
summary(lm(mpg~wt+drat,mtcars))
cat("--------","\n")
mylm(mpg~wt+drat,mtcars,"summary")
cat("--------","\n")
all.equal(unname(mylm(mpg~wt+drat,mtcars,"nothing")$coefficients[,1]),unname(lm(mpg~wt+drat,mtcars)$coefficients), tolerance = 1e-6)
```

```{r}
#predictlm
n <- nrow(mtcars)
train_n <- floor(n*0.7)
traindata <- mtcars[1:train_n, ]#the original data set
testdata <- mtcars[(train_n+1):n, ]#the new data set
mylm1 <- mylm(mpg~wt,traindata,"nothing")
lm1 <- lm(mpg~wt,traindata)
all.equal(sum(predictlm(mylm1,testdata)-predict(lm1,testdata)), 0, tolerance = 1e-6)
```

### Efficiency
I compare the efficiency between `mylm` and `summary.lm`. `mylm` has a lower efficiency. 

```{r}
system.time(for(i in 1:100)
  mylm(mpg~wt+drat,mtcars,"nothing"))
system.time(for(i in 1:100)
  summary(lm(mpg~wt+drat,mtcars)))
```

I also compare the efficiency between `predictlm` and `predict.lm`. The efficiency of `predictlm` is a bit lower than `predict.lm`. 

```{r}
n <- nrow(mtcars)
train_n <- floor(n*0.7)
traindata <- mtcars[1:train_n, ]#the original data set
testdata <- mtcars[(train_n+1):n, ]#the new data set
system.time(for(i in 1:100)
  predictlm(mylm(mpg~wt+drat,mtcars,"nothing"),testdata))
system.time(for(i in 1:100)
  predict(lm(mpg~wt+drat,traindata),testdata))
```
